chronos_splines

### 2017-12-27 analysis/chronos/analysis_splines.Rmd
add resilience analysis to splines RWI

# Preparar datos para computar RWI 
```{r}
source(paste0(di, 'script/R/computeSpline.R'))
```

@@

year_sampledepth <- year_sampledepth %>% 
  mutate(site_sorted = case_when(
    site == "sj" ~ "0_sj", 
    site == "caH" ~ "1_caH",
    site == "caL" ~ "2_caL")
```

@@

@@

>>>>

# Preparar datos para computar RWI 
```{r}
source(paste0(di, 'script/R/computeSpline.R'))
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/rwiResilience.R'))
```

@@

year_sampledepth <- year_sampledepth %>% 
  mutate(site_sorted = case_when(
    site == "sj" ~ "0_sj", 
    site == "caH" ~ "1_caH",
    site == "caL" ~ "2_caL"))
```

@@

# Resilience

* Computar métricas de resiliencia RWI para los tres sitios. 
* Computar tres eventos climáticos: 1995, 2005, 2012
* Computar ventanas temporales: 2, 3 y 4

## Aggregate RWI by tree

* Agregar valores medios de RWI por site (obtenemos sj_tree / caL_tree, caH_tree) 
* ver fun rw_byTree (utilizada para bai_resilience.Rmd)

```{r}
# Remember snc = structure of core name SJ0101 (site | tree | core)
rwi_sj_tree <- rw_byTree(rwi_sj, snc =c(2,2,2), locname = 'SJ')
rwi_caL_tree <- rw_byTree(rwi_caL, snc =c(2,2,2), locname = 'CA')
rwi_caH_tree <- rw_byTree(rwi_caH, snc =c(2,2,2), locname = 'CA')
```

```{r}
# Drought years 
dyears <- c(1995, 2005, 2012)

# SJ 
res_4_sj <- rwiResilience(bai_sj, event_years = dyears, window = 4)
res_3_sj <- rwiResilience(bai_sj, event_years = dyears, window = 3)
res_2_sj <- rwiResilience(bai_sj, event_years = dyears, window = 2)

# caL
res_4_caL <- rwiResilience(bai_caL, event_years = dyears, window = 4)
res_3_caL <- rwiResilience(bai_caL, event_years = dyears, window = 3)
res_2_caL <- rwiResilience(bai_caL, event_years = dyears, window = 2)

# caH
res_4_caH <- rwiResilience(bai_caH, event_years = dyears, window = 4)
res_3_caH <- rwiResilience(bai_caH, event_years = dyears, window = 3)
res_2_caH <- rwiResilience(bai_caH, event_years = dyears, window = 2)
```

dyears <- c(1995, 2005, 2012)
event_years <- dyears
window = 4

rwiResilience <- function(rwi_tree, event_years)

  out_rwi <- c() 
  out_res <- c() 
  out <- list()

  require(dplyr)

  for (i in event_years){
    # Create df previous, during and post event
    df <- rwi_tree %>% 
      mutate(year = as.numeric(row.names(.))) %>% as.data.frame()

    df_pre <- df %>% filter(year < i & year >= (i - window)) %>% mutate(disturb = 'pre')
    df_event <- df %>% filter(year == i) %>% mutate(disturb = 'dr')
    df_post <- df %>% filter(year > i & year <= (i + window)) %>% mutate(disturb = 'post')

    # Melt data 
    dfmelt <- bind_rows(df_pre, df_event, df_post) %>% 
      gather(tree, value, -disturb, -year)

    # Compute mean of RWI (previous, during and posterior)
    rwi_df <- dfmelt %>% group_by(disturb, tree) %>% 
      summarise(mean_period = mean(value),
                sd_period = sd(value),
                se_period = sd_period/sqrt(length(value))) %>% 
      mutate(disturb_year = i) %>% as.data.frame()

    out_rwi <- rbind(out_rwi, rwi_df)

    # Compute resilience by trees 
    aux_resilience <- c() 
    trees <- unique(rwi_df$tree)

    for (t in trees){
      # Filter by tree
      df_tree <- rwi_df %>% filter(tree == t)

      # Compute resilience metrics by tree
      aux_df <- df_tree %>% dplyr::select(-c(tree, sd_period, se_period)) %>% 
        spread(key=disturb, value=mean_period) %>% 
        mutate(rt = dr / pre,
               rc = post / dr,
               rs = post / pre,
               rrs = ((post - dr) / pre),
               tree = t) %>% 
        dplyr::select(rt, rc, rs, rrs, disturb_year, tree) %>% as.data.frame()

      aux_resilience <- rbind(aux_resilience, aux_df)
    }

    out_res <- rbind(out_res, aux_resilience)
  }

  out$rwi <- out_rwi
  out$resilience <- out_res

    return(out)
}

i <- 1995
rwi_tree <- rwi_sj_tree

@@

## Download data from E-OBS
# http://www.ecad.eu/download/ensembles/download.php#datafiles

library(loadeR)

# Define dir and list nc files 
mydir <- '/Users/ajpelu/Downloads/climaobs'

list.files(mydir, pattern = "\\.nc$")

di <- dataInventory("/Users/ajpelu/Downloads/climaobs/tg_0.25deg_reg_v16.0.nc")
